\section{Abstract}
Cryptocurrencies (\textit{digital assets designed to work as mediums of exchange})
permit users to securely send money without trusting any other human intermediary
or any other centralised third-party system or institution, such as a bank, to
verify those transactions\footnote{https://en.wikipedia.org/wiki/Cryptocurrency}.
Instead the strong cryptography and mathematics inherent in the software
algorithms secure the peer-to-peer network and safeguard against forgeries and
ensures transaction finality. The network of participating nodes together
creates the blockchain where all transactions and balances are recorded and
ensures network immutability. This is a truly transforming technology and has
the potential to benefit people across the globe. However, the blockchains in
classic cryptocurrencies (\textit{such as Bitcoin}) are transparent public
ledgers that are accessible to anyone and the full transaction history is
preserved and the blockchain is readily available for analysis\footnote{https://www.respublica.org.uk/disraeli-room-post/2015/03/24/bitcoin-is-not-anonymous/}. This presents a very serious issue for users online and financial privacy.
Even though the pseudonymous users of classic blockchains are not directly
associated with their real-world identities, every transaction among these
pseudonyms is potentially traceable and every transaction is recorded for
all posterity and for \underline{anyone} to access and view.
\\
\\
In this white-paper, we present \textbf{Spectrecoin}; a cryptocurrency that
uses a range of advanced cryptographic techniques, such as dual-key stealth
addresses and ring-signatures to achieve un-linkable and un-traceable
private and confidential transactions on its blockchain. \textbf{Spectrecoin}
also comprises a novel privacy-preserving consensus mechanism,
‘\textbf{\textit{Proof-of-Anonymous-Stake}}’ that let its users retain
full privacy as they support the network by running the software and
staking their coins. \textbf{Spectrecoin} also protects the user’s online
identity by integrating TOR (\textit{The Onion Router})\footnote{https://www.torproject.org/} 
in the software and is therefore a
comprehensive privacy focused cryptocurrency. \textbf{Spectrecoin} also
retains the ability to conduct ‘\textit{open}’ public transactions
(\textit{much like Bitcoin}) and this may serve certain use cases and
blockchain audit-ability. \textbf{Spectrecoin} provides the best of both
worlds, total privacy and public transactions, without any compromise.
In this paper we present the current technology and functionality of
\textbf{Spectrecoin} to the common reader with some experience and knowledge
of blockchain and cryptocurrencies. We also discuss how we achieve
confidential and privacy maintaining consensus and we discuss what
\textbf{Spectrecoin} aims to achieve in the future. Further references
to explain and expand on certain topics are included within the text as
footnotes.
