\section{The ‘ATXO\_Set’ Dilemma}

We can say that all the ATXOs created in the same transaction are part 
of an ‘\textit{ATXO\_Set}’, i.e. they will forever be linked to each 
other as they were created at the same time and it can be assumed that 
they all belong to the same user. There will always be multiple outputs 
per transaction because of the denomination system, because amounts 
have to be split into discrete values. 



The following dilemma may then occur; the ATXO picking algorithm (as it is 
now) could select ATXOs from an ‘\textit{ATXO\_SET}‘ as ‘\textit{mixins}‘ 
in a ring-signature and this could potentially compromise privacy by making 
the signature more susceptible to deductive analysis. In other words, an 
observer could be able to determine which of the ‘\textit{mixins}‘ are fake. 



\subsection{Solutions}
New algorithms have been created to negate these issues and strengthen the 
privacy of the network. This way depending on the random pick of the initial
‘\textit{mixins}‘ and the denominations to fill, there will be a random 
amount of ‘\textit{mixins}‘ from the same transaction in the final transaction. 



This will also ensure that each output is only used once as a ‘\textit{mixin}‘ 
in one of the ring-signatures (VINs). Something which was previously only 
assured by chance. Same ‘\textit{mixin}‘ in different VINs can only be fake. 



\begin{itemize}
	\item When the first 9 ‘\textit{mixins}‘ for an output are chosen, it is 
	completely random, but is ensured that all ‘\textit{mixins}‘ come from 
	different transactions.
	\item When ‘\textit{mixins}‘ for the second ring-signature are chosen, 
	there is a 33\% chance that the algorithm tries to 	choose outputs from 
	the transaction chosen as ‘\textit{mixins}‘ for the first ring-signature. 
	If no outputs can 	picked that way, a new random output is chosen and 
	the corresponding transaction is added as new source of ‘\textit{mixins}‘.
	\item Repeat.
\end{itemize}



We believe that these issues also exist in Monero and other CryptoNote based 
systems and may have been described first in a paper entitled 
\textit{“A Traceability Analysis of Monero’s Blockchain”}
\footnote{https://eprint.iacr.org/2017/338.pdf} and in particular in 
chapter: 5.2 Heuristic II: Leveraging Output Merging in this paper.
