\chapter{Bug Bounty Program}
We are introducing the first stage of our bug bounty program that will cover 
serious or critical bugs and we will later expand on this to include bounties 
for smaller bugs as well. We are putting up the bounties to make the 
Spectrecoin software better and more secure and we believe that active 
participation by the community will help to achieve this and benefit us all.



If you believe you have found a bug or a problem with the Spectrecoin 
software, submit a report (details below) and contribute to making 
Spectrecoin more secure. However, before you submit a bug report, please 
search our GitHub and other sources to see if the problem has already 
been reported / discovered. If the issue has not been described anywhere, 
then follow the instructions at the end of this document for how to submit 
the bug you have found. Please do not report critical vulnerabilities 
publicly.



\section{Bug Bounties and Rewards}
\begin{description}
	\item[£1000] Deanonymise Spectrecoin (SPECTRE $<>$ SPECTRE) 
	transactions. (\textit{Proof that a protocol is not anonymous, 
	i.e. a flaw in the implementation of ring signatures or the stealth 
	address technology}).
	\item[£1000] Deanonymise TOR as implemented in Spectrecoin and real 
	IP address leakage. (\textit{Proof that you can identify a real IP 
	address on the network}). This relates to the implementation of TOR 
	in the Spectrecoin software ONLY and not bugs in the TOR software.
\end{description}



The bounties will be paid out in XSPEC to the equivalent value at the time 
of a submission. All the bugs / errors found need to relate to and identify 
faulty source code (in the ‘master’ branch), not just reported issues that 
you experience without being able to relate this to specific code. 



Contact the developers privately by sending an e-mail to xspec @ protonmail.ch 
(delete the spaces ofc) or DM the developers directly on Discord (@Tek or 
@Helix) with the details of the issue. Do not post the issue on GitHub or 
anywhere else until the issue has been resolved. Ideally you would create 
a pull-request on GitHub in the proper repository with the necessary fix 
and make the developers aware.
