\section{Disclaimer}
\textbf{The Alias software} and the source code is being developed 
and maintained by an independent collective of blockchain enthusiasts.
The Alias collective does not hold any personal information on any users of the
Alias software and will never ask for any identifying information
from any user in order to download and use the software. The Alias collective
does not gather any personal data. \textbf{The Alias collective will NEVER ask
users for their private keys, wallet / data files or any other information 
that could enable us to access a user’s fund or wallet or identify the
user.} The Alias collective does not hold any kind of key / information / data
or have any other means or technology that would enable it to analyse
transactions on the Alias blockchain with a view to identify any
user. The creation of the Alias network did not involve any trusted
setup and no personal information was ever collected. No person associated with the Alias collective process any kind of personal data and we do not believe any relevant data protection laws apply. We would be happy to assist with any formal request from any relevant authority but would have to inform them that we do not hold any data and that we are unable to conduct any kind of network analysis.
\\
\\
The Alias collective understands and appreciates that the Alias software 
holds and protects your money and we take this responsibility seriously. The Alias collective is doing everything it can to make sure that the network and
the software is as secure as it can be. However, the software comes with
no guarantees and must be considered experimental. In general, confidentiality
and privacy should never be considered as an absolute and users should do their
own due diligence and risk assessment and take whatever measures they deem
appropriate to protect themselves online. When conducting a risk assessment
with regards to your own privacy online; consider that we do not have
conclusive knowledge of any possible adversary’s capabilities or resolve to
achieve their aims. The Alias collective does not in any shape or form condone any illegal activity and Alias has not been created to facilitate any kind
of illegal activity. If we would become aware of any illegal activity we would inform the relevant authority without fail.
\\
\\
The Alias collective is not responsible in any way whatsoever for any lost password, hacking, acts of God, war, natural disasters or any other
 unforeseen event
that could compromise the network and cause any loss of funds. The Alias collective
cannot be held responsible for any users incompetence or recklessness that may
result in any loss or liability. The current parameters of the software are set
according to how we believe the network should operate, but network parameters
and characteristics could change if deemed necessary. The Alias collective will always
work to increase the privacy of the Alias software, increase the value of
the company and hence the value of your investment. All decisions are made with
this in mind. This is not investment advice and we do not offer any investment
or financial advice. Alias could be worth zero and you could loose all your money.
\\
\\
If you own Alias and you run a Alias wallet, it is strongly
recommended that you always keep up to date with developments and always run
the latest version of the software. This is best done by either subscribing
to our Discord server\footnote{https://discord.gg/ckkrb8m} or use 
Blockfolio\footnote{https://blockfolio.com/}.
