\section{Notes}
ALIAS can be sent in a public transaction or a private transaction.
For the purpose of this document a public transaction will send ALIAS (public)
(\textit{public-ALIAS}) and a private transaction will send ALIAS (private) (\textit{private-ALIAS}). (p)ALIAS transactions employs well known
technology albeit used in creative ways and
some parts of the White-paper is to a large degree referencing already
published material from various sources. The newly added section on
‘\textbf{\textit{Anonymous-Proof-of-Stake}}’ however is unique to this
White-paper and an original ALIAS (private) technology. There is no scope in
this document to discuss cryptography or mathematics and the author is
neither a cryptographer nor a mathematician. The descriptions of cryptographic
functions are taken from the relevant source documents that are referenced
throughout this document and if you are so inclined you can read up on the
details. This is not meant as an academic paper or as a reference document
but rather as a brief description of the ALIAS (private) network and the
underlying technology used. This document does not intend to contribute
to the debate about privacy online and this discussion is beyond the scope
of this document. We simply believe that we have an absolute right to
privacy in our financial affairs online as we do in the real world and
so our ideology is also simple; to provide real decentralised resilient
privacy and confidentiality on the blockchain and offer provable private
transactions for users.
