\chapter{Roadmap}
Below we set out the development goals for the next 12 months. We are 
primarily focused on improving and optimising the privacy technology, 
wallet security and the roadmap will reflect this.



\section{Seed word (BIP32)}
Creation and restoration of private keys with seed words (BIP32). This will 
provide a secure backup solution where the seed words are all you need to 
recover your wallet in case of some kind of data loss. This could also form 
the basis of integration with hardware 
wallets.\footnote{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}



\section{Cold Staking}
Cold staking allows you to assign your staked value (\textit{the value of 
your coins}) to a cold staking node. This cold staking node can then stake 
on your behalf, but without being able to access or spend your coins. In 
other words, cold staking allows you to stake with coin values being 
stored offline and without giving the cold staking node operator access 
to your coins (\textit{usually, the operator would be the owner of the 
coins being staked, although this is not mandatory}). This would also 
allow for staking pools in the future.\footnote{https://particl.news/cold-staking-pools-what-you-need-to-know-beb57951c3f3}



\section{Android mobile wallet}
We will deliver an Android mobile wallet, but the detailed specifications 
are not yet determined. This will be the first stage of our mobile 
development and should not be considered the final mobile solution.



\section{Windows and Mac OSX installers}
Installer for MacOS \& Windows will come.



\section{Network security}
We will keep exploring options for network security and it appears likely 
that the focus might be on some implementation of
Dandelion++\footnote{https://arxiv.org/abs/1805.11060} in the future. 
This will further decrease the ability of an attacker to analyse network 
traffic.
